---
title: "A few helper functions for working with trees"
output: github_document 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(data.tree)

source("tree_utils.R")
```


dependencies on 

- `data.tree` by Christoph Glur for converting data between tree representations and dataframes
- `networkD3` by Christopher Gandrud, JJ Allaire, Kent Russell, & CJ Yetman for representing series of tree levels as Sankey diagrams
- `tidyverse` by Hadley Wickham et al. for dataframe manipulations 

## Example Data: SomeCo org charts

A simple org chart with department names and id in the same table (ID is just a truncated MD5 hash of the department name)

```{r}
df <- read_csv("SomeCoOrg.csv")
df %>% kable()
```

## `naive_level_order` - Organize a DF to make it most likely a Tree can be resolved

What if we get a levelized tree, but the columns are not arranged left-to-right higher-to-lower level (the order used by `data.tree::FromDataFrameTable`)?
`naive_level_order` takes the df and orders columns by least to most distinct values (which approximates the LtoR HtoL order described above).
```{r naive_level_order}
set.seed(1234)
randomized_df <- df %>% select(sample(names(df %>% select(ends_with("Name"), "Unit ID"))))
randomized_df %>% kable()
randomized_df %>% naive_level_order() %>% kable()
```




## `equivalent_leaves` - search a tree for nodes with the same leaves as a node in another tree 
```{r equivalent_nodes}

id_tree <-  df %>% naive_level_order() %>% select(ends_with("ID")) %>% df_to_tree()
name_tree <- df %>% naive_level_order() %>% select(ends_with("Name"), "Unit ID") %>% df_to_tree()
print(name_tree)
print(id_tree)
equivalent_leaves(id_tree, name_tree) %>% kable()
equivalent_leaves(name_tree, id_tree) %>% kable()

```

`equivalent_leaves` also has a `verbose` parameter to inspect the search

```{r}

equivalent_leaves(name_tree, id_tree, verbose=TRUE) %>% kable()

```

